SimSurvey demo

### 2022-01-26 tutorial/tutorial.Rmd
Improve index predictions from sdmTMB in tutorial

## Expand grid data for predictions
grid_dat <- as_tibble(select(survey$grid_xy, x, y, depth)) %>% distinct()
grid_dat <- purrr::map_dfr(sort(unique(dat$year)), ~ bind_cols(grid_dat, year = .))
grid_dat$offset <- mean(dat$offset)

## Predict across full grid and get index
tow_area <- survey$setdet$tow_area[1] # cell and tow area is consistent in the simulation
cell_area <- survey$setdet$cell_area[1]
pred <- predict(fit, newdata = grid_dat, return_tmb_object = TRUE, area = cell_area / tow_area)
index <- get_index(pred)

@@

## Visualize result
index %>% 
  plot_ly(x = ~year, color = ~type, legendgroup = ~type) %>% 
  add_ribbons(ymin = ~lwr, ymax = ~upr, line = list(width = 0), showlegend = FALSE) %>% 
  add_lines(y = ~N)

@@

## DROP DATA FROM STRATA 5 AND 6 FOLLOWING YEAR 10
survey$setdet <- filter(survey$setdet, !(year > 10 & strat %in% 5:6))

@@

## Visualize result
index %>% 
  plot_ly(x = ~year, color = ~type, legendgroup = ~type) %>% 
  add_ribbons(ymin = ~lwr, ymax = ~upr, line = list(width = 0), showlegend = FALSE) %>% 
  add_lines(y = ~N)

>>>>

## Expand grid data for predictions
grid_dat <- as_tibble(select(survey$grid_xy, x, y, depth)) %>% distinct()
grid_dat <- purrr::map_dfr(sort(unique(dat$year)), ~ bind_cols(grid_dat, year = .))
grid_dat$offset <- 0

## Predict across full grid and get index
cell_area <- survey$setdet$cell_area[1]
pred <- predict(fit, newdata = grid_dat, sims = 1000)
index <- get_index_sims(pred, area = rep(cell_area, nrow(pred)))

@@

## Visualize result
index %>% 
  plot_ly(x = ~year, color = ~type, legendgroup = ~type) %>% 
  add_ribbons(ymin = ~lwr, ymax = ~upr, line = list(width = 0), showlegend = FALSE) %>% 
  add_lines(y = ~N, line = list(dash = ~ifelse(type == "True", "solid", "dot")))

@@

## DROP DATA FROM STRATA 5, 6 FOLLOWING YEAR 10
survey$setdet <- filter(survey$setdet, !(year > 10 & strat %in% 5:6))

@@

## Visualize result
index %>% 
  plot_ly(x = ~year, color = ~type, legendgroup = ~type) %>% 
  add_ribbons(ymin = ~lwr, ymax = ~upr, line = list(width = 0), showlegend = FALSE) %>% 
  add_lines(y = ~N, line = list(dash = ~ifelse(type == "True", "solid", "dot"))) %>% 
  add_segments(x = 10, xend = 10, y = 0, yend = max(index$upr, na.rm = TRUE) * 1.05, 
               inherit = FALSE, showlegend = FALSE, hoverinfo = "none", color = I("black"),
               size = I(0.5), linetype = I(2))
